% ==================================
%           Chapter 1C.2
%  Investigating the Causes of CVDs
%      Created by Michael Tang
%            2025.01.13
% ==================================

\subsubsection{1C.2 Investigating the Causes of CVDs}
\paragraph{Designing Studies}
\begin{itemize}
    \item \textbf{Purpose:}
    \begin{itemize}
        \item Investigate one factor or variable while controlling others.
        \item Larger sample sizes yield more statistically significant results.
    \end{itemize}
    \item \textbf{Longitudinal Studies:} Follow the same group of individuals over many years to observe long-term patterns.
    \item \textbf{Meta-Analysis:} Combines results from multiple studies for more reliable data.
\end{itemize}

\paragraph{Designing and Evaluating Studies}
\begin{itemize}
    \item \textbf{Key Criteria:}
    \begin{itemize}
        \item \textbf{Valid:} The study answers the questions it sets out to address.
        \item \textbf{Precise:} Measurements are consistent and have little variation.
        \item \textbf{Reliable:} Results can be reproduced by other scientists.
    \end{itemize}
    \item \textbf{Factors Affecting Reliability:}
    \begin{itemize}
        \item Who funded the study?
        \item Were measurements biased or affected by external interests?
    \end{itemize}
    \item \textbf{Importance:} Evaluation ensures practical applications in health and research are based on \underline{robust}
    (坚固的) evidence.
\end{itemize}

\paragraph{Risk Factors for Cardiovascular Diseases (CVDs)}
\textbf{Non-Modifiable Risk Factors:}
\begin{itemize}
    \item \textbf{Genetics:}
    \begin{itemize}
        \item \underline{Inherited tendency} (遗传趋势) for heart disease.
        \item Example: Twin studies show a higher likelihood of heart disease in identical twins than \underline{fraternal}
        (兄弟的) twins.
    \end{itemize}
    \item \textbf{Age:} Older individuals have reduced \underline{elasticity} (弹性) in arteries, leading to higher CVD risk.
    \item \textbf{Gender:}
    \begin{itemize}
        \item Men are more likely to develop CVDs than \underline{pre-menopausal women} (绝经前妇女).
        \item \underline{Oestrogen} (雌性激素) in women reduces plaque build-up, offering some protection before
        \underline{menopause} (绝经期).
    \end{itemize}
\end{itemize}