% ===========================
%       Chapter 1A.1
%  Velocity and Acceleration
%   Created by Michael Tang
%        2025.01.14
% ===========================

\subsubsection{1A.1 Velocity and Acceleration}
\paragraph{Rate of Movement}
\begin{itemize}
    \item \textbf{Speed}
    \begin{itemize}
        \item Formula:
        \begin{equation}
            \begin{split}
                \text{Speed} (\unit{m.s^{-1}}) &= \frac{\text{Distance} (\unit{m})}{\text{Time} (\unit{s})} \\
                v &= \frac{d}{t}
            \end{split}
        \end{equation}
        \item \underline{Scalar quantity} (标量, magnitude only).
    \end{itemize}
    \item \textbf{\underline{Velocity} (速度)}
    \begin{itemize}
        \item Formula:
        \begin{equation}
            \begin{split}
                \text{Velocity} (\unit{m.s^{-1}}) &= \frac{\text{\underline{Displacement} (位移量)} (\unit{m})}{\text{Time}
                (\unit{s})} \\
                v &= \frac{\Delta s}{\Delta t}
            \end{split}
        \end{equation}
        \item \underline{Vector quantity} (矢量, include magnitude and direction).
    \end{itemize}
    \item \textbf{\underline{Displacement} (位移量)}
    \begin{itemize}
        \item Defined as the shortest straight-line distance in a specific direction between the start and end points.
        \item Example: The displacement of an athlete running 300 m around a track but ending 75 m north of the start point is 75
        m due north.
    \end{itemize}
\end{itemize}

\paragraph{\underline{Scalar} (标量) and \underline{Vector} (向量) Quantities}
\begin{itemize}
    \item \textbf{Scalar:} Magnitude only (e.g., speed, distance, mass).
    \item \textbf{Vector:} Magnitude and direction (e.g., velocity, displacement, \underline{acceleration} 加速度).
\end{itemize}

\paragraph{Average and \underline{Intantaneous Speed} (瞬时速度)}
\begin{itemize}
    \item \textbf{Average Speed:} Accounts for variations in speed over a period of time.
    \begin{equation}
        \text{Average Speed} (\unit{m.s^{-1}}) = \frac{\text{Total Distance} (\unit{m})}{\text{Total Time} (\unit{s})}
    \end{equation}
    \item \textbf{Instantaneous Speed:} The speed of an object at a specific instant in time.
\end{itemize}

\paragraph{\underline{Acceleration} (加速度)}
\begin{itemize}
    \item \textbf{Definition:} The rate of change of velocity.
    \item \textbf{Formula:}
    \begin{equation}
        \begin{split}
            \text{Acceleration} (\unit{m.s^{-2}}) &= \frac{\text{Change in Velocity} (\unit{m.s^{-1}})}{\text{Time} (\unit{s})} \\
            a &= \frac{\Delta v}{\Delta t} \\
            &= \frac{v - u}{t}
        \end{split}
    \end{equation}
    where: $a$ = acceleration, $v$ = final velocity, $u$ = initial velocity, $t$ = time taken.
    \item \textbf{Key Notes:}
    \begin{itemize}
        \item Positive acceleration: Speeding up.
        \item Negative acceleration (deceleration): Slowing down.
    \end{itemize}
\end{itemize}